Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-26 astronum_2018/astronum-xrb.tex
more text

@@

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run.
The top panel shows the temperature.  The initial perturbation reached
to $2\times 10^4~\mathrm{cm}$, so at this point, the extent of the
burnt region has nearly doubled.  The flame structure is quite wide,
since there are multiple burning stages beyond just helium to carbon, and
this shows up in the composition.

>>>>

\newcommand{\isot}[2]{$^{#2}\mathrm{#1}$}

\newcommand{\gcc}{\mathrm{g~cm^{-3} }}
\newcommand{\cms}{\mathrm{cm~s^{-1} }}

@@

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run
at 0.007~s.  The burning layer is only about 10~m high.  Underneath is
\isot{Ni}{56}, representative of the underlying neutron star, and
above it is very a low density ($10^{-4}~\gcc$) buffer.  Only a
portion of the vertical extent is show.  The top panel shows the
temperature.  The initial perturbation reached to $2\times
10^4~\mathrm{cm}$, so at this point, the extent of the burnt region
has nearly doubled.  The flame structure is quite wide, since there
are multiple burning stages beyond just helium to carbon, and this
shows up in the composition.  This is seen more clearly in the lower
panel which shows the mean molecular weight of the nuclei ($\bar{A}$).
We see the further behind the head of the flame we are, the heavier
the ash nuclei.  The second panel shows the energy generation rate.
It is strongest just above the neutron star surface, behind the flame.
We also see that the head of the flame is ``detached'' from the base
of the atmosphere, with the strongest burning at the head of the flame
slightly higher up in the atmosphere.  This can also be more clearly
seen in the last panel that shows the ash structure.  This appears
reminiscent of the flame structure seen in the earlier simulations of
\cite{cavecchi:2012} \MarginPar{Yuri, would you agree?}  The third
panel shows the velocity through the plane of the simulation---this is
induced by the Coriolis force as the burning front spreads laterally.
A tight hurricane structure has setup as a result of the flame
spreading.  This is the geostrophic balance discussed in
\cite{SPIT_ETAL02}.  Finally, as already mentioned, the last panel
shows the ash composition.  These calculations are ongoing and will be
the subject of a detailed study in the near future.
